\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage}

% Set section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%==================== HEADER ====================
\begin{center}
    {\LARGE \textbf{John Doe}} \\
    \vspace{5pt}
    \href{mailto:johndoe@example.com}{johndoe@example.com} | +123 456 7890 | \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} | \href{https://github.com/johndoe}{github.com/johndoe}
\end{center}

\vspace{15pt}

%==================== EDUCATION ====================
\section*{Education}
\noindent\textbf{Bachelor of Science in Computer Science} \\
\textit{University of Example} \hfill \textbf{2018 -- 2022} \\
\begin{itemize}[leftmargin=*]
    \item GPA: 3.8/4.0
    \item Relevant Courses: Data Structures, Algorithms, Operating Systems, Machine Learning
\end{itemize}

%==================== EXPERIENCE ====================
\section*{Experience}
\noindent\textbf{Software Engineer Intern} \hfill \textbf{Summer 2021} \\
\textit{TechCorp Solutions, Inc.} \\
\begin{itemize}[leftmargin=*]
    \item Developed and maintained features for a web-based application using JavaScript, React, and Node.js.
    \item Improved API performance by optimizing database queries, reducing response times by 20\%.
    \item Collaborated with a cross-functional team to design scalable microservices architecture.
\end{itemize}

\noindent\textbf{Teaching Assistant} \hfill \textbf{Fall 2020 -- Spring 2021} \\
\textit{University of Example, Department of Computer Science} \\
\begin{itemize}[leftmargin=*]
    \item Assisted in teaching Data Structures and Algorithms course for 60+ students.
    \item Held weekly office hours to help students with assignments and exam preparation.
    \item Graded homework and provided feedback to students to improve their understanding.
\end{itemize}

%==================== PROJECTS ====================
\section*{Projects}
\noindent\textbf{Personal Portfolio Website} \hfill \textbf{2022} \\
\begin{itemize}[leftmargin=*]
    \item Developed a responsive personal website using HTML, CSS, and JavaScript to showcase projects.
    \item Integrated GitHub API to dynamically display recent commits and project activity.
\end{itemize}

\noindent\textbf{Smart Home Automation System} \hfill \textbf{2021} \\
\begin{itemize}[leftmargin=*]
    \item Built a smart home system using Raspberry Pi, Python, and IoT sensors for remote monitoring.
    \item Created a mobile app with React Native to control home devices via WiFi.
\end{itemize}

%==================== SKILLS ====================
\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} C, C++, Python, JavaScript, SQL
    \item \textbf{Web Technologies:} React, Node.js, HTML, CSS
    \item \textbf{Tools:} Git, Docker, Jenkins, AWS
\end{itemize}

%==================== AWARDS & CERTIFICATIONS ====================
\section*{Awards \& Certifications}
\begin{itemize}[leftmargin=*]
    \item Certified AWS Solutions Architect -- Associate, 2022
    \item Dean's List, University of Example, 2019 -- 2021
\end{itemize}

%==================== FOOTER ====================
\begin{center}
    \vspace{20pt}
    \small{\textit{References available upon request.}}
\end{center}

\end{document}
